Follow-up Samples

### 2016-08-02 Baxter_followUps_2016.Rmd
added legend for stage figure

```{r diff_by_stage, echo=FALSE, cache=TRUE, fig.height=5, fig.width=6}
# Make training set with samples without follow ups
train <- merge(metaI, shared, by.x='sample', by.y='Group')
train <- train[-which(train$sample %in% metaF$initial),]
train <- train[, c('lesion',colnames(train)[grep('Otu[0123456789]', colnames(train))])]

@@

layout(matrix(c(1,2,3,4), nrow=1))
par(mar=c(5,3,1,0.5))
#non advanced
plot(0, type='n', xlim=c(0.75,2.25), ylim=c(0,1.1), ylab='Probability of lesion (OTU model)', xaxt='n', xlab='')
mtext(text='Nonadvanced\nAdenoma', at=c(1.5), side=1, line=4, font=2)
axis(1, at=c(1,2,3,4), labels=c('Baseline','Follow-up','Baseline','Follow-up'))
stripchart(at=1, initial_probs[metaF$Dx=='Adenoma'], pch=21, bg='orange', cex=1.2, lwd=0.5, vertical=T, add=T)
stripchart(at=2, follow_probs[metaF$Dx=='Adenoma'], pch=21, bg='orange', cex=1.2, lwd=0.5, vertical=T, add=T)
segments(1, initial_probs[metaF$Dx=='Adenoma'], 2, follow_probs[metaF$Dx=='Adenoma'], col='orange')
ade_p<-t.test(initial_probs[metaF$Dx=='Adenoma'], follow_probs[metaF$Dx=='Adenoma'], paired=T, alternative='greater')$p.value
text(1.5, 1, sprintf('p=%.1g',ade_p))

@@

>>>>

```{r diff_by_stage, echo=FALSE, cache=TRUE, fig.height=4, fig.width=7}

# Make training set with samples without follow ups
train <- merge(metaI, shared, by.x='sample', by.y='Group')
train <- train[-which(train$sample %in% metaF$initial),]
train <- train[, c('lesion',colnames(train)[grep('Otu[0123456789]', colnames(train))])]

@@

layout(matrix(c(1,2,3,4), nrow=1))
par(mar=c(5,3,1,0.5), mgp=c(1.5,0.5,0))
#non advanced
plot(0, type='n', xlim=c(0.75,2.25), ylim=c(0,1.1), ylab='Probability of lesion (OTU model)', xaxt='n', xlab='')
mtext(text='Nonadvanced\nAdenoma', at=c(1.5), side=1, line=4, font=2)
axis(1, at=c(1,2,3,4), labels=c('Baseline','Follow-up','Baseline','Follow-up'))
stripchart(at=1, initial_probs[metaF$Dx=='Adenoma'], pch=21, bg='orange', cex=1.2, lwd=0.5, vertical=T, add=T)
stripchart(at=2, follow_probs[metaF$Dx=='Adenoma'], pch=21, bg='orange', cex=1.2, lwd=0.5, vertical=T, add=T)
segments(1, initial_probs[metaF$Dx=='Adenoma'], 2, follow_probs[metaF$Dx=='Adenoma'], col='orange')
ade_p<-t.test(initial_probs[metaF$Dx=='Adenoma'], follow_probs[metaF$Dx=='Adenoma'], paired=T, alternative='greater')$p.value
text(1.5, 1, sprintf('p=%.1g',ade_p))

@@

There doesn't seem to be a difference in the outcome of the model by stage.
